### 2008-03-24 doc/arch-spiral-poincare.tkz.tex
Archimedes spiral in Poincaré model. Illustrations.

\begin{figure}[p]
  \centering
  \begin{tikzpicture}[scale=3.5]
    \coordinate [label=left:$O$] (O) at (0, 0) {};

    % Klein disk itself
    \draw[thick] (O) circle(1);

    \begin{scope}[decoration={
        markings,
        mark=at position .12
        with \coordinate[] (P){};}]

      % Poincare Archimedes spiral
      \draw[postaction={decorate}] (O) plot[parametric,samples=100,domain=0:12.56,id=exp,smooth]
                function{cos(t)*(1-2/(exp(t)+1)),sin(t)*(1-2/(exp(t)+1))};

    \end{scope}

    \path[very thin,draw=gray] (O)-- node[sloped,above]{$\rho_p=\phi$} (P);

    % dot marks
    \foreach \p in {P,O} \draw node[dot] at (\p) {};
  \end{tikzpicture}
  \caption{Спираль Архимеда $\rho_p(\phi)=\phi$ в модели Пуанкаре}
  \label{fig:arch-spiral-poincare}
\end{figure}