### 2008-04-13 doc/coth.tkz.tex
Further major edits in geodesics section; study only $t>0$ case,

\begin{figure}[thb]
  \centering
  \begin{tikzpicture}[scale=1.4,axis/.style={draw=gray,thin},samples=50,smooth]
    \draw[->,axis] (-0.2,0) -- (5.5,0) node[below left] {$t$};
    \draw[->,axis] (0,-0.2) -- (0,5.5) node[below left] {$f(t)$};

    \begin{scope}[domain=0.2:4]
      \draw[thick] plot[id=cth] function{cosh(x)/sinh(x)} node[above] {$\cth{t}$};
      \draw plot[id=cth2] function{cosh(x)/(2.2*sinh(x))} node[right] {$\frac{\cth{t}}{C_1}$};
    \end{scope}

    % cut out interval
    \coordinate[label=below left:$0$] (M) at (0,0) {};
    \coordinate[label=below:$t_0$] (N) at (0.49,0) {};
    \draw[very thick, densely dashed] (M)--(N);
    \draw[densely dotted] (N) -- ($ (N)+(0,1) $);

    % asymptote
    \draw[dashed] plot[id=one,domain=0:5] function{1};

    \node[left] at (0,1) {$1$};
  \end{tikzpicture}
  \caption{Функции $f(t) = \cth(t)$ и $f(t) = \frac{\cth(t)}{C_1},\,
    C_1>1,\,t>0$}
  \label{fig:coth}
\end{figure}