### 2008-04-15 doc/geodesics-hyperbolic-2.tkz.tex

\begin{figure}[!thb]
  \centering
  \begin{tikzpicture}[samples=50,smooth]
    \coordinate[label=left:$O$] (O) at (0,0) {};

    \begin{scope}[raw gnuplot]
      \foreach \p in {0,1,2,3,4,5,6,7,8,9,10,11}
               \draw plot function{set polar; set parametric; plot [0.54930615:2.5] asin(cosh(t)/(2*sinh(t)))+\p*pi/6,t;}
                     plot function{set polar; set parametric; plot [0.54930615:2.5] pi-asin(cosh(t)/(2*sinh(t)))+\p*pi/6,t;};
    \end{scope}

    \node[dot] at (O) {};
  \end{tikzpicture}
  \caption[Геодезические линии с разными значениями параметра
  $C_2$]{Геодезические линии с разными значениями параметра $C_2$ при
    \mbox{$C_1=2$}}
  \label{fig:geodesics-hyperbolic-2}
\end{figure}